Using algorithmic skeletons in EcmaScript to parallelize computation in browsers through Web Workers

### 2015-05-09 docs/paper/paper.tex
Added some things

\subsection{Results}
The results for the benchmark are the displayed in Tab.~\ref{tab:benchmark} and Figure~\ref{fig:relative} shows the relative performance of the parallel approach compared to the sequential one.
\begin{table}
  \centering
  \begin{tabular}{|r|c|c|}
    \hline
    Elements & Serial [ops/sec] & Parallel [ops/sec] \\
    \hline
    100 & \textbf{154442} & 377.2\\
    1,000 & \textbf{17460.2} &  368.4 \\
    10,000 & \textbf{1768.6} & 311.2 \\
    100,000 & \textbf{179.2} & 172.2 \\
    1,000,000 & 16.96 & \textbf{33.2} \\
    \hline
  \end{tabular}
  \caption{Comparing p-j-s (parallel) and plain JS (serial) performance for an image transformation.}
  \label{tab:benchmark}
\end{table}

@@

>>>>

\subsection{Results}
The results for the benchmark are the displayed in Tab.~\ref{tab:benchmark}. Based on those results, we created a chart (Figure~\ref{fig:relative}) that shows the relative performance of the parallel approach compared to the sequential one.
\begin{table}
  \centering
  \begin{tabular}{|r|c|c|}
    \hline
    Elements & Serial [ops/sec] & Parallel [ops/sec] \\
    \hline
    100 & \textbf{154442} & 377.2\\
    1,000 & \textbf{17460.2} &  368.4 \\
    10,000 & \textbf{1768.6} & 311.2 \\
    100,000 & \textbf{179.2} & 172.2 \\
    1,000,000 & 16.96 & \textbf{33.2} \\
    \hline
  \end{tabular}
  \caption{Comparing p-j-s (parallel) and plain JS (serial) performance for an image transformation.}
  \label{tab:benchmark}
\end{table}

@@

\subsubsection*{Acknowledgments.}
Thanks to Rosa Wachenhauzer, our tutor, for reviewing this paper and also for all her support and guidance throughout this entire project.
